Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-08-16 paper/paper.tex
more stuff

\subsection{Interlude: Rethinking the Action-State-Reward model of RL}
Barto proposes to decouple extrinsic rewards (i.e generated by the external environment) from intrinsic reward (generated from withing the "organism")
biologically, extrinsic rewards would correspond to so-called "sensations"
while intrinsic rewards would correspond to "reward signals".

Thus there are two environments: the external environment, and the internal environment built-into the "organism". The organism takes highly level DECISIONS (the DMN can confortably sit here!) which act on the internal environment (this environment probably corresponds to low-level subsystems like motor, etc.) which then transform theses  into ACTIONS executed in the external environment. The external environment generates sensations which get mapped into reward signals (via the internal environment), etc.

@@

\begin{mdframed}
\paragraph*{Why MDPS ?} At this point, it is righteous to question the applicability of MPDs as a model for something as complex as human behavior ?
Indeed a critique could argue that Markov chains are state-machines without memory. These may describe insects, or other behaviorally primitive beings like ATM machines, insects, etc., but won't be sufficient to describe human beings, as for example, human behavior is heavily influenced not only by the current state but by past states as well (memory).

\paragraph*{Answer:} We emphasize that the brain in general, and the DMN in particular,
is a physical system governed by the laws of
physics and can be formally described
by Markov processes at a sufficiently coarse scale.
It has indeed been previously proposed \citep{tegmark2016improved} that
any system obeying the laws of classical physics can be accurately modeled as a Markov process as long as the time
step is sufficiently short.

Rational probabilistic planning can be reformulated
as a standard memory Markov process by simply expanding the
definition of the state $s$ to include experience episodes of the past.
This adds the capacity for memory, since then, the next state depends not only on the current state but also on a finite number of past states. This is precisely what partially observable MDPs do ~\citep{starkweather2017dopamine,o2006making,o2006making}.

Also, it should be noted that MDPs have been successfully used as neural model for animal behavior. One can mention ~\citep{Rao2010}, just to name a few.
\end{mdframed}

>>>>

@@

\paragraph*{Interlude: Rethinking the Action-State-Reward model of RL.}
Barto proposes to decouple extrinsic rewards (i.e generated by the external environment) from intrinsic reward (generated from withing the "organism")
biologically, extrinsic rewards would correspond to so-called "sensations"
while intrinsic rewards would correspond to "reward signals".

Thus there are two environments: the external environment, and the internal environment built-into the "organism". The organism takes high-level DECISIONS (the DMN can confortably sit here!) which act on the internal environment (this environment probably corresponds to low-level subsystems like motor, etc.) which then transform theses  into ACTIONS executed in the external environment. The external environment generates sensations which get mapped into reward signals (via the internal environment), etc.

\begin{mdframed}
\paragraph*{Why MDPS ?} At this point, it is righteous to question the applicability of MPDs as a model for something as complex as human behavior.
Indeed a critique could argue that Markov chains are state-machines without memory. These may describe insects, or other behaviorally primitive beings like ATM machines, insects, etc., but won't be sufficient to describe human beings, as for example, human behavior is heavily influenced not only by the current state but by past states as well (memory).

\paragraph*{Answer:}
\begin{itemize}
  \item First, let us emphasize that the brain in general, and the DMN in particular,
is a physical system governed by the laws of
physics and can be formally described
by Markov processes at a sufficiently coarse scale.
It has indeed been previously proposed \citep{tegmark2016improved} that
any system obeying the laws of classical physics can be accurately modeled as a Markov process as long as the time
step is sufficiently short.

\item Rational probabilistic planning can be reformulated
as a standard memory Markov process by simply expanding the
definition of the state $s$ to include experience episodes of the past.
This adds the capacity for memory, since then, the next state depends not only on the current state but also on a finite number of past states. This is precisely what partially observable MDPs do ~\citep{starkweather2017dopamine,o2006making}.

\item Also, it should be noted that MDPs have been successfully used as neural model for animal behavior. One can mention ~\citep{Rao2010} (random dots), ~\citep{Valton2011} (mal-adaptive decision-making in a rat version of a gambling task) just to name a few.

\item Successes in AI/ML: \citep{ng2004,abbeel2004,mnih2015,silver2016mastering,pritzel2017neural}

\end{itemize}
\end{mdframed}
